% Andrey Kaipov
% Resume
% Adapated from https://github.com/moderncv/moderncv/blob/master/template.tex

\documentclass[10pt,letterpaper,sans]{moderncv} % choose a4 or letterpaper
\usepackage[vscale=.89,hscale=.80]{geometry} % page margins

\input{patches/preamble}
\moderncvstylecustom[black][awesome]{classic}{banking}

\name{Andrey}{Kaipov}
\homepage{kaipov.com}
\email{andrey@kaipov.com}

\begin{document}
\makecvtitle
\vspace{-2mm}

\section{Experience}
\cventryoneline{June 2020 -- Present}{Sr Site Reliability Engineer}{Ultimate Kronos Group}{Weston, FL}{}{
  Cloud Services
  \begin{itemize}
  \item
      Develop and maintain internal Terraform modules abstracting development
      teams' access to public cloud services, integrating with our private cloud
      services API, and helping them transition into the public cloud.
  \item
      Developed a CLI and workflow system to automate the management of volume
      snapshots and backups for our MySQL and MongoDB services to meet our audit
      deadlines, which were actually nonexistent at the time.
  \end{itemize}
  %
  Developer Experience
  \begin{itemize}
  \item
      Worked closely with traditional Windows sysadmins and application owners
      to automate the heavily involved and manual configuration of our core
      products via Ansible playbooks, teaching SRE principles along the way.
  \end{itemize}
}
\cventryoneline{Jan 2020 -- Apr 2020}{Site Reliability Engineer}{Magic Leap}{Plantation, FL}{}{
  Launch Coordination
  \begin{itemize}
  \item
      Developed Kubernetes operators to manage GCP resources, extending our
      internal PaaS to help our product teams transition from AWS to GCP.
  \item
      Evangelized the technologies of our SRE sister-squads to our product
      teams, while helping them transition to newer company-wide standards.
  \item
      Performed housekeeping across the SRE organization -- upgraded Terraform
      AWS and GCP modules and projects to use the latest versions, upgraded
      Concourse pipelines, migrated images from ECR and GCR to our private
      Docker registry, and added reusable features to our internal tooling for
      our product teams.
  \end{itemize}
}
\cventryoneline{Jan 2017 -- Jan 2020}{Site Reliability Engineer}{Ultimate Software}{Weston, FL}{}{
  Cloud Platform \& Observability
  \begin{itemize}
  \item
      Developed and managed a centralized logging, metrics, and alerting
      platform for company-wide, ingesting over 5TB/day of logs and metrics into
      our multi-datacenter Elasticsearch and InfluxDB clusters.
  \item
      Managed several VM and container-based orchestration platforms for product
      teams to leverage, including a homegrown PaaS, on-prem Pivotal Cloud
      Foundry, and on-prem Kubernetes clusters.
  \item
      Partnered with product teams to help developers learn about our
      infrastructure and internal tooling, and to help productionalize their
      applications and processes.
  \end{itemize}
}
\cventryoneline{Summer 2016}{Software Engineer Intern}{Best Buy}{Richfield, MN}{}{}

\section{Skills}
\cventryskill{Languages}
  {Go, Shell, JavaScript, TypeScript, Python, Ruby, Java, \LaTeX.}
\cventryskill{Tooling}
  {Docker, Terraform, Packer, Vault, Ansible, Chef, Bosh, Concourse, GitLab.}
\cventryskill{Services}
  {MySQL, MongoDB, Redis, RabbitMQ.}
\cventryskill{Platforms}
  {Linux, Kubernetes, Cloud Foundry, OpenStack, GCP, AWS.}
\cventryskill{Observability}
  {Elasticsearch, Logstash, Kibana, Fluent Bit, InfluxDB, Telegraf, Grafana, Sensu.}

\section{Projects}
\cventryproject{kaipov.com}{goobs}
  {Go client library for an OBS Studio websockets server.}
\cventryproject{kaipov.com}{funcopgen}
  {Generate functional options for your Go structs.}
\cventryproject{kaipov.com}{env2conf}
  {Convert environment variables into configuration.}
\cventryproject{kaipov.com}{active-standby}
  {Kubernetes controller supporting active/standby applications.}
\cventryproject{kaipov.com}{mongodb-pool}
  {Manage MongoDB connection pools with less headaches.}
\cventryproject{kaipov.com}{tf-chef-solo}
  {Chef Solo provisioner for Terraform, inspired by the Packer one.}
\cventryproject{kaipov.com}{website}
  {An over-engineered website \& resume; you're reading part of it right now!}

\section{Education}
\cventryoneline{Aug 2013 -- Dec 2016}{BS in Mathematics \& Computer Science}{Florida International University}{Miami}{FL}{
  Honors: Summa Cum Laude, Phi Beta Kappa, FIU Ambassador Scholar, Florida Academic Scholar.
}

\end{document}
